Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
evaluation summary

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{myref}
\usepackage{url}
\usepackage{pgfplots}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\subsection{Labeled Training and Ground Truth}

@@

@@

Summarize the evaluation. One sentence per subsection.

\emph{Overfitting and other machine learning issues} Yao-Yuan, how do we avoid
these?

\emph{Language choice} We only showed that this technique works for Python 3.
However, \cite{learning-to-blame} uses a similar technique to great effect in
OCaml, and if it works on these two quite-different languages then we believe
it would work on others as well. Additionally, Python is a common choice of
language for introductory programming courses, so even a technique that worked
only on Python would still be very useful for helping novices.

\emph{Target population} We don't know exactly who our study population is -
who wrote the programs in the dataset and what exactly they were trying to write.
It is likely that they are primarily students and not professional software engineers,
and thus possible that our technique does not generalize well to the kinds of
bugs that would be found in an industrial setting rather than an educational one.

\emph{Automatic labeling} Since our dataset is so large, we were forced to use an automatic
scheme to label bugs rather than marking them by hand. We chose to use the diffs
between each program that crashes and the next program that does not, but this method
is not 100\% accurate because the next program may contain additional changes
beyond what was needed to fix the bug, or it may indeed be an entirely unrelated
program. We mitigate this problem by discarding as outliers program pairs that have
changed too much. We also note that if our `true' accuracy is indeed a little
smaller than our reported accuracy because of this effect, then the `true' baseline
is also lower than the reported baseline for the same reason, so our
\emph{margin} of effectiveness is unlikely to change much.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{myref}
\usepackage{url}
\usepackage{framed}
\usepackage{pgfplots}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

@@

\subsection{Labeled Training and Ground Truth}
\label{sec-training}

@@

Although our evaluation demonstrates that our algorithm scales to
accurately localize Python errors in lage datasets, our results may not
generalize to all use cases.

\emph{Overfitting.} Since our algorithm makes use of supervised machine
learning, one threat to validity is overfitting (i.e., learning a model
that is too complex with respect to the data and thus fails to generalize).
We mitigate this threat by using cross-validation, as discussed in
\secref{training}.

\emph{Language choice.} We have only demonstrated that our technique works
for Python 3. We hypothesize that it should apply to similar
dynamically-typed languages, such as Ruby, but such evaluations remain
future work. We mitigate this threat slightly by constructing our algorithm 
so that it does not depend on Python-specific features or node types
(e.g., in \secref{slice-algorithm} we explicitly omit relatively ``exotic'' 
features such as generators, ``yield'' and coroutines that may not always
be present in other languages).

\emph{Target population.} Unlike many other studies that focus specifically
on students, we have very little information about the makeup of our
subject population. The general popularity of PythonTutor is an advantage
for collecting a large, indicative dataset, but it does mean that we have
no specific information about the programmers or the programs they were
trying to write. In general the website targets beginners rather than
professional software engineers. As a result, our technique may not
generalize well to the kinds of bugs that would be found in an industrial
setting rather than a novice or educational one.

\emph{Ground truth.} The size of our dataset precluded the manual annotation 
of each buggy program. Instead, we used historical successful
edits from actual users as our ground truth notion of the desired fault
localization. This has the advantage of aligning our algorithm with user
intuitions in cases where there are multiple logically-consistent answers
(see \secref{motex}), and thus increasing the utility of our tool. However,
this definition of ground truth may be overly permissive: the next
correct program in the historical sequence may contain additional spurious
changes beyond those strictly needed to fix the bug.
We mitigate this problem by discarding as outliers program pairs that have
changed too much. \fixme{Really? This is the first time WRW is hearing
about this. If this is true, you have to go back and mention this earlier
where we talk about ground truth definitions and data set selection.}

@@

We evaluated our results on over 270,000 pairs of beginner-written Python
programs. Our primary research result relates to accuracy: 
\begin{framed}
\noindent Our algorithm is very accurate, implicating the correct program
terms 60--79\% of the time (for Top-1 to Top-3 lists), compared to the
Python interpreter's 45\% accuracy. 
\end{framed} 
In addition, we investigated the design decisions of our algorithm:
\begin{framed}
\noindent All feature categories (i.e., static, dynamic, and contextual)
were critical, as measured by Gini importance, ANOVA F-score
and a leave-one-out analysis. 
\end{framed}
Finally, we investigated the sensitivity of our algorithm to various
contexts:
\begin{framed}
\noindent Our algorithm generalizes, with similar accuracy across the top
error types and on a dataset that is more diverse than that of related
work.
\end{framed}
